---
title: "Calculating Risk Ratios"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculating Risk Ratios}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(knitr.table.format = "html") 
library(juryR)
```

All of the models in this package are binomial logistic regressions. They can be summarized using the base R function `summary()`.

```{r}
summary(lr_caused)
```

If a more presentation-ready summary is desired, the `summ` function from the [`jtools`](https://jtools.jacob-long.com) package works well.

```{r}
jtools::summ(lr_caused)
```

The odds ratios of each model, along with a 95% confidence interval, can be calculated using the following:

```{r}
calculate_risk(lr_caused)
```

To reproduce the figures as they are seen in the paper, the following code can be used:

```{r}
calculate_risk(lr_caused) |> 
  kableExtra::kable(digits = 3) |> 
  kableExtra::kable_classic(full_width = FALSE, html_font = "Cambria")
```

